A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-06-28 reviews/EJOR/02/ResponsetoReviewers.tex

\documentclass{article}

\title{Response to reviewers}
\author{A game theoretic model of the behavioural gaming that takes \\
place at the ED-EMS interface}

\begin{document}
    \maketitle

    The authors would like to thank once again all the reviewers for their
    constructive feedback and for
    the time they took to review the manuscript.
    Please find the summary of the changes made:

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1: \textit{The following two papers are related to the
        current work and I suggest the authors add them in the references with
        citations in the literature review: \\
        1. Chen, W., Z. G. Zhang, and X. Chen. 2020. "On Two-tier Healthcare
        System Under Capacity Constraint." International Journal of Production
        Research 58 (12): 3744-3764. \\
        2. Wang, J., Z. Wang, Z. G. Zhang and F. Wang. 2021.
        ``Efficiency-quality trade-off in allocating resource to public
        healthcare systems.'' International Journal of Production Research, \\
        DOI:10.1080/00207543.2021.1992529}
    \end{itemize}

    These two papers are now cited in the manuscript at the literature review
    section.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 2: I gave a look into the new version and the comments
        made by the authors following the reviews they received.
        My criticism towards the paper as stated in the first round stays.
        It is basically the question of what are the standards of EJOR.
        If a paper which states a interesting model and gives details on
        numerical procedures for solving it but without any theorems and
        insights is good enough, then it should be accepted as the paper is
        doing a good job of what it promises.
        Otherwise, they should look for a more applied journal where what they
        do is sufficient.
    \end{itemize}

    Here's a list of reasons of why I think this paper should be considered for
    publication in EJOR.
    Firstly, reviewer 2 states that the paper does not provide any insights.
    We would like to point out that this paper does provide theoretical results
    and insights.
    Section 3 provides detailed theoretical expressions of the queueing model's
    performance measures.
    Expressions of the waiting time, blocking time and proportion of
    individuals within target have been derived and are presented in the paper.
    Also, section 4.2 contains a list of applied scenarios where insights 
    are presented.
    A busy model is examined and insights on ways to increase the relative
    efficiency of the model are presented.

    Secondly here is a list of papers already published in EJOR that introduce
    a new model and give details on numerical procedures for solving it but
    without any new theorems:
    \begin{itemize}
        \item A queueing model for general group screening policies and dynamic
        item arrivals \\
        https://doi.org/10.1016/j.ejor.2010.05.042
        \item Selfish routing in public services: \\
        https://doi.org/10.1016/j.ejor.2013.04.003
        \item The effect of ambulance relocations on the performance of
        ambulance service providers \\
        https://doi.org/10.1016/j.ejor.2015.12.022
        \item Robust and stochastic formulations for ambulance deployment and
        dispatch \\
        https://doi.org/10.1016/j.ejor.2019.05.011
        \item A Markovian queueing model for ambulance offload delays \\
        https://doi.org/10.1016/j.ejor.2012.11.030
        \item Models and algorithms for an integrated vessel scheduling and tug
        assignment problem within a canal harbor \\
        https://doi.org/10.1016/j.ejor.2021.10.037
        \item The application of operational research to European air traffic
        flow management - understanding the context \\
        https://doi.org/10.1016/S0377-2217(99)00084-3
    \end{itemize}

    Finally, note that the aims and scope of EJOR do not emphasise that a paper
    should present a new theorem in order to be published.
    Here's the aim and scope of EJOR as listed in their website: \\[0.5cm]
    \textit{
        The European Journal of Operational Research (EJOR) publishes high
        quality, original papers that contribute to the methodology of operational
        research (OR) and to the practice of decision making. EJOR contains the
        following types of papers:
        \begin{itemize}
            \item Invited Reviews, explaining to the general OR audience the developments in an OR topic over the recent years
            \item Innovative Applications of OR, describing novel ways to solve real problems
            \item Theory and Methodology Papers, presenting original research results contributing to the methodology of OR and to its theoretical foundations,
            \item Short Communications, if they correct important errors found in papers previously published in EJOR
        \end{itemize}
    }

\end{document}

### 2022-06-28 reviews/EJOR/02/ResponsetoReviewers.tex

\documentclass{article}

\title{Response to reviewers}
\author{A game theoretic model of the behavioural gaming that takes \\
place at the ED-EMS interface}

\begin{document}
    \maketitle

    The authors would like to thank once again all the reviewers for their
    constructive feedback and for
    the time they took to review the manuscript.
    We are also pleased to see that the reviewers feel that the revision has addressed their comments and that the manuscript presents scientifically correct and useful results.
    We have made the remaining requested minor changes and also provide a response to one of the 
    reviewers whose remaining concern is about the fit of this paper for EJOR.

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1: \textit{The following two papers are related to the
        current work and I suggest the authors add them in the references with
        citations in the literature review: \\
        1. Chen, W., Z. G. Zhang, and X. Chen. 2020. "On Two-tier Healthcare
        System Under Capacity Constraint." International Journal of Production
        Research 58 (12): 3744-3764. \\
        2. Wang, J., Z. Wang, Z. G. Zhang and F. Wang. 2021.
        ``Efficiency-quality trade-off in allocating resource to public
        healthcare systems.'' International Journal of Production Research, \\
        DOI:10.1080/00207543.2021.1992529}
    \end{itemize}

    These two papers are now cited in the manuscript at the literature review
    section.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 2: I gave a look into the new version and the comments
        made by the authors following the reviews they received.
        My criticism towards the paper as stated in the first round stays.
        It is basically the question of what are the standards of EJOR.
        If a paper which states a interesting model and gives details on
        numerical procedures for solving it but without any theorems and
        insights is good enough, then it should be accepted as the paper is
        doing a good job of what it promises.
        Otherwise, they should look for a more applied journal where what they
        do is sufficient.
    \end{itemize}

    We are grateful for the opportunity to respond to this as it seems that the 
    remaining concern is the fit of this work in EJOR and not the work itself.
    Firstly, this paper does provide theoretical results
    and insights.
    Section 3 provides detailed theoretical expressions of the queueing model's
    performance measures.
    Expressions of the waiting time, blocking time and proportion of
    individuals within target have been derived and are presented in the paper.
    Also, section 4.2 contains a list of applied scenarios where insights 
    are presented.
    A busy model is examined and insights on ways to increase the relative
    efficiency of the model are presented.

    We do understand the main point being raised by the reviewer in that this paper is not a purely theoretic one.
    For the benefits of the handling editor who we believe is left with the decision of whether or not the paper is in the scope of EJOR, here is a list of a number of papers published in EJOR that have a similar applied emphasis:
    \begin{itemize}
        \item A queueing model for general group screening policies and dynamic
        item arrivals \\
        https://doi.org/10.1016/j.ejor.2010.05.042
        \item Selfish routing in public services: \\
        https://doi.org/10.1016/j.ejor.2013.04.003
        \item The effect of ambulance relocations on the performance of
        ambulance service providers \\
        https://doi.org/10.1016/j.ejor.2015.12.022
        \item Robust and stochastic formulations for ambulance deployment and
        dispatch \\
        https://doi.org/10.1016/j.ejor.2019.05.011
        \item A Markovian queueing model for ambulance offload delays \\
        https://doi.org/10.1016/j.ejor.2012.11.030
        \item Models and algorithms for an integrated vessel scheduling and tug
        assignment problem within a canal harbor \\
        https://doi.org/10.1016/j.ejor.2021.10.037
        \item The application of operational research to European air traffic
        flow management - understanding the context \\
        https://doi.org/10.1016/S0377-2217(99)00084-3
    \end{itemize}

### 2022-06-28 reviews/EJOR/02/ResponsetoReviewers.tex

\usepackage{amssymb}

\title{Response to reviewers}
\author{A game theoretic model of the behavioural gaming that takes \\
place at the ED-EMS interface}

\begin{document}
    \maketitle

    The authors would like to thank once again all the reviewers for their
    constructive feedback and for
    the time they took to review the manuscript.
    We are also pleased to see that the reviewers feel that the revision has
    addressed their comments and that the manuscript presents scientifically
    correct and useful results.
    We have made the remaining requested minor changes and also provide a
    response to one of the reviewers whose remaining concern is about the fit
    of this paper for EJOR.
    Our main arguments are:
    \begin{itemize}
        \item Our paper provides theoretical results and insights
        \item There is a number of pages in EJOR that are similar to ours
        \item The EJOR scope does not emphasise that a paper should present a
        new theorem in order to be published
    \end{itemize}

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1: \textit{The following two papers are related to the
        current work and I suggest the authors add them in the references with
        citations in the literature review: \\
        1. Chen, W., Z. G. Zhang, and X. Chen. 2020. "On Two-tier Healthcare
        System Under Capacity Constraint." International Journal of Production
        Research 58 (12): 3744-3764. \\
        2. Wang, J., Z. Wang, Z. G. Zhang and F. Wang. 2021.
        ``Efficiency-quality trade-off in allocating resource to public
        healthcare systems.'' International Journal of Production Research, \\
        DOI:10.1080/00207543.2021.1992529}
    \end{itemize}

    These two papers are now discussed and included in the literature review
    section.

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 2: I gave a look into the new version and the comments
        made by the authors following the reviews they received.
        My criticism towards the paper as stated in the first round stays.
        It is basically the question of what are the standards of EJOR.
        If a paper which states a interesting model and gives details on
        numerical procedures for solving it but without any theorems and
        insights is good enough, then it should be accepted as the paper is
        doing a good job of what it promises.
        Otherwise, they should look for a more applied journal where what they
        do is sufficient.
    \end{itemize}

    We are grateful for the opportunity to respond to this as it seems that the 
    remaining concern is the fit of this work in EJOR and not the work itself.
    Firstly, this paper does provide theoretical results
    and insights.
    Section 3 provides detailed theoretical expressions of the queueing model's
    performance measures.
    Expressions of the waiting time, blocking time and proportion of
    individuals within target have been derived and are presented in the paper.
    Also, section 4.2 contains a list of applied scenarios where insights 
    are presented.
    A busy model is examined and insights on ways to increase the relative
    efficiency of the model are presented.

    We do understand the main point being raised by the reviewer in that this
    paper is not a purely theoretic one.
    For the benefits of the handling editor who we believe is left with the
    decision of whether or not the paper is in the scope of EJOR, here is a
    list of examples of papers published in EJOR that have a similar applied
    emphasis:
    \begin{itemize}
        \item[$\rhd$] \textbf{A queueing model for general group screening
        policies and dynamic item arrivals} published in 2010, Volume 207,
        Issue 2, by Dieter Claeys, Joris Walraevens, Koenraad Laevens and
        Herwig Bruneel \\
        https://doi.org/10.1016/j.ejor.2010.05.042
        \item[$\rhd$] \textbf{Selfish routing in public services} published in
        2013, Volume 230, Issue 1, by Vincent A.Knight and Paul R. Harper \\
        https://doi.org/10.1016/j.ejor.2013.04.003
        \item[$\rhd$] \textbf{The effect of ambulance relocations on the
        performance of ambulance service providers} published in 2016, Volume
        252, Issue 1, by T. C. van Barneveld, S. Bhulai and R.D.van der Mei \\
        https://doi.org/10.1016/j.ejor.2015.12.022
        \item[$\rhd$] \textbf{Robust and stochastic formulations for ambulance
        deployment and dispatch} published in 2019, Volume 279, Issue 2, by
        Dimitris Bertsimas and Yeesian Ng \\
        https://doi.org/10.1016/j.ejor.2019.05.011
        \item[$\rhd$] \textbf{A Markovian queueing model for ambulance offload
        delays} published in 2013, Volume 226, Issue 3, by Eman Almehdawe, Beth
        Jewkes and Qi-Ming He \\
        https://doi.org/10.1016/j.ejor.2012.11.030
        \item[$\rhd$] \textbf{Models and algorithms for an integrated vessel
        scheduling and tug assignment problem within a canal harbor} published
        in 2022, Volume 300, Issue 3, by Matteo Petris, Paola Pellegrini and
        Raffaele Pesenti \\
        https://doi.org/10.1016/j.ejor.2021.10.037
        \item[$\rhd$] \textbf{The application of operational research to
        European air traffic flow management - understanding the context}
        published in 2000, Volume 123, Issue 1, by Paula Leal de Matos and
        Richard Ormerod \\
        https://doi.org/10.1016/S0377-2217(99)00084-3
    \end{itemize}

    Finally, we note that the aims and scope of EJOR do not emphasise that a paper
    should present a new theorem in order to be published.
    Here's the aim and scope of EJOR as listed in their website: \\[0.5cm]
    \textit{
        The European Journal of Operational Research (EJOR) publishes high
        quality, original papers that contribute to the methodology of operational
        research (OR) and to the practice of decision making. EJOR contains the
        following types of papers:
        \begin{itemize}
            \item[$\square$] Invited Reviews, explaining to the general OR audience the developments in an OR topic over the recent years
            \item[$\square$] Innovative Applications of OR, describing novel ways to solve real problems
            \item[$\square$] Theory and Methodology Papers, presenting original research results contributing to the methodology of OR and to its theoretical foundations,
            \item[$\square$] Short Communications, if they correct important errors found in papers previously published in EJOR
        \end{itemize}
    }

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3: \textit{The authors handled my remarks well.}
    \end{itemize}
    Thank you.

### 2022-07-01 sections/literature_review/main.tex
Address all reviewers comments from second revision (#46)
* Add editor and reviewers comments

* Add suggested references in lit review

* Update known words

* Apply suggestion by proselint

* Add response to reviewers

* Apply suggestions from code review

Co-authored-by: Vince Knight <vince@vknight.org>

* Further minor changes

- Add main arguments for publishing our paper to editor
- Include authors, date published and Volume/issue on previous papers
- Add response to reviewer 3
- Minor rewords

* Update known words

* Update known words again

* Fix minor typo

Co-authored-by: Vince Knig

In the above models, the players are attempting to increase their share of 
individuals choosing to queue.
In public healthcare type settings, this is not 
necessarily the case. 
Rational usage of public services will not necessarily lead to a socially
optimal outcome.
Rather, the overall service needs to be considered as players aim to minimise
their experienced congestion.
In~\cite{sadat2015can} a healthcare application was studied where patients 
could choose between two hospitals, where a utility function is derived that is
based on patients' perceived quality of life.
In~\cite{knight2013selfish} the authors place the individuals' choices between
different public services 
within the formulation of routing games and measure inefficiencies using a 
concept known as the price of anarchy (PoA)~\cite{koutsoupias1999worst}.
They show that the price of anarchy increases with worth of service and that is
low for systems with insufficient capacities.
In~\cite{TwoTierHealthcareSystem} a two-tier healthcare system with a capacity
constrained is studied where patients can choose between two systems to receive
their service.
The first system is labelled as the free system (public government-funded
hospital) which offers service without seeking any profit and the second one is
the toll system (private hospital) that aims to maximise its own profit.
The authors, also compare the two-tier system with its one-tier equivalent,
where only the free system exists.
In~\cite{knight2017measuring} a normal form game is built that is informed by a 
two-dimensional Markov chain in order to model interactions between critical
care units.
In~\cite{EfficiencyQualityTradeOff} a queueing-game-theoretical model is
introduced where there are two types of service providers; a high quality
highly-congested hospital and a low quality low-congested hospital.
The authors study a two-stage Stackelberg game where the government is the
\textit{leader} and the arriving patients are the \textit{followers}.
In~\cite{deo2011centralized} the authors study the network effect of ambulance 
diversion by proposing a non-cooperative game between two EDs that are modelled
as a queueing network.
Each ED's objective is to minimise its own waiting time and chooses a diversion
threshold based on the patients it has.
In equilibrium both EDs choose to divert ambulances in order to avoid getting
arrivals from the other ED.
In this paper this concept is extended by allowing the ambulance service to 
decide how to distribute its patients among the two EDs.
The players of the game are both the hospitals and the customers of the
hospitals, as opposed to the previous models which are one or the other.
Thus, the novelty of our work is combining both these aspects.

>>>>

In the above models, the players are attempting to increase their share of 
individuals choosing to queue.
In public healthcare type settings, this is not 
necessarily the case. 
Rational usage of public services will not necessarily lead to a socially
optimal outcome.
Rather, the overall service needs to be considered as players aim to minimise
their experienced congestion.
In~\cite{sadat2015can} a healthcare application was studied where patients 
could choose between two hospitals, where a utility function is derived that is
based on patients' perceived quality of life.
In~\cite{knight2013selfish} the authors place the individuals' choices between
different public services 
within the formulation of routing games and measure inefficiencies using a 
concept known as the price of anarchy (PoA)~\cite{koutsoupias1999worst}.
They show that the price of anarchy increases with worth of service and that is
low for systems with insufficient capacities.
In~\cite{TwoTierHealthcareSystem} a two-tier healthcare system with a capacity
constrained is studied where patients can choose between two systems to receive
their service.
The first system is labelled as the free system (public government-funded
hospital) which offers service without seeking any profit and the second one is
the toll system (private hospital) that aims to maximise its own profit.
The authors, also compare the two-tier system with its one-tier equivalent,
where only the free system exists.
In~\cite{knight2017measuring} a normal form game is built that is informed by a 
two-dimensional Markov chain in order to model interactions between critical
care units.
In~\cite{EfficiencyQualityTradeOff} a queueing-game-theoretical model is
introduced where there are two types of service providers; a high quality
high-congested hospital and a low quality low-congested hospital.
The authors study a two-stage Stackelberg game where the government is the
\textit{leader} and the arriving patients are the \textit{followers}.
In~\cite{deo2011centralized} the authors study the network effect of ambulance 
diversion by proposing a non-cooperative game between two EDs that are modelled
as a queueing network.
Each ED's objective is to minimise its own waiting time and chooses a diversion
threshold based on the patients it has.
In equilibrium both EDs choose to divert ambulances in order to avoid getting
arrivals from the other ED.
In this paper this concept is extended by allowing the ambulance service to 
decide how to distribute its patients among the two EDs.
The players of the game are both the hospitals and the customers of the
hospitals, as opposed to the previous models which are one or the other.
Thus, the novelty of our work is combining both these aspects.
